Inference of proto-neutron star properties from gravitational wave data in core-collapse supernovae.

### 2020-09-23 simulations.tex
update

{For the {\it test set}, we use $8$ axisymmetric (2D) simulations using the AENUS-ALCAR code
(see Table~\ref{Tab:2dSimList} for a list of models).
$7$ of these simulations use a selection of progenitors with masses in the range} $M_{\mathrm{ZAMS}} = 11.2 - 40 \, \Msol$
 evolved through the hydrostatic phases by
\cite{Woosley_Heger_Weaver__2002__ReviewsofModernPhysics__The_evolution_and_explosion_of_massive_stars}.
We performed one simulation of each stellar model using the equation
of state of \cite{Lattimer_Swesty__1991__NuclearPhysicsA__LS-EOS} with
an incompressibility of $K = 220 \, \mathrm{MeV}$ (LS220) and added
comparison simulations with the SFHo EOS
\cite{Steiner_et_al__2013__apj__Core-collapseSupernovaEquationsofStateBasedonNeutronStarObservations}
and the EOS of
\cite{Shen_et_al__2011__prc__Newequationofstateforastrophysicalsimulations}
(GShen) for the {progenitor} with $M_{\mathrm{ZAMS}} = 15 \, \Msol$. To this set of
simulations, we add the waveform of a two-dimensional model used in
\cite{Torres:2019a}, denoted \texttt{s20S}. It corresponds to a star
with the same initial mass, $M_{\mathrm{ZAMS}} = 20 \, \Msol$, as for
one of the other 7 axisymmetric simulations, but was taken from a
newer set of stellar-evolution models
\cite{Woosley_Heger__2007__physrep__Nucleosynthesisandremnantsinmassivestarsofsolarmetallicity}.
It was evolved with the SFHo EOS.

{For all the simulations,} we mapped the pre-collapse state of the stars to a spherical
coordinate system with $n_r = 400$ zones in radial direction
distributed logarithmically with a minimum grid width of
$(\Delta r)_{\mathrm{min}} = 400 \, \mathrm{m}$ and an outer radius of
$r_{\mathrm{max}} = 8.3 \times 10^{9} \, \mathrm{cm}$ and
$n_{\theta} = 128$ equidistant cells in angular direction. For the
neutrino energies, we used a logarithmic grid with $n_e = 10$ bins up
to $240 \, \mathrm{MeV}$.
\pcd{Unlike the model set, the simulations in the test set cannot be 1D becase we need to 
extract the gravitational wave signal, which is a multi-dimensional effect. For each simulation
we extract the gravitational wave signal, $h_+(t)$,  by means of the quadrupole formula and compute the 
time evolution of the surface gravity, $r(t)$.}

>>>>

{For the {\it test set}, we use $8$ axisymmetric (2D) simulations using the AENUS-ALCAR code
(see Table~\ref{Tab:2dSimList} for a list of models).
$7$ of these simulations use a selection of progenitors with masses in the range} $M_{\mathrm{ZAMS}} = 11.2 - 40 \, \Msol$
 evolved through the hydrostatic phases by
\cite{Woosley_Heger_Weaver__2002__ReviewsofModernPhysics__The_evolution_and_explosion_of_massive_stars}.
We performed one simulation of each stellar model using the equation
of state of \cite{Lattimer_Swesty__1991__NuclearPhysicsA__LS-EOS} with
an incompressibility of $K = 220 \, \mathrm{MeV}$ (LS220) and added
comparison simulations with the SFHo EOS
\cite{Steiner_et_al__2013__apj__Core-collapseSupernovaEquationsofStateBasedonNeutronStarObservations}
and the GShen EOS 
\cite{Shen_et_al__2011__prc__Newequationofstateforastrophysicalsimulations}
for the {progenitor} with $M_{\mathrm{ZAMS}} = 15 \, \Msol$. To this set of
simulations, we add the waveform of a two-dimensional model used in
\cite{Torres:2019a}, denoted \texttt{s20S}. It corresponds to a star
with the same initial mass, $M_{\mathrm{ZAMS}} = 20 \, \Msol$, as for
one of the other 7 axisymmetric simulations, but was taken from a
newer set of stellar-evolution models
\cite{Woosley_Heger__2007__physrep__Nucleosynthesisandremnantsinmassivestarsofsolarmetallicity}.
It was evolved with the SFHo EOS.

{For all the simulations,} we mapped the pre-collapse state of the stars to a spherical
coordinate system with $n_r = 400$ zones in radial direction
distributed logarithmically with a minimum grid width of
$(\Delta r)_{\mathrm{min}} = 400 \, \mathrm{m}$ and an outer radius of
$r_{\mathrm{max}} = 8.3 \times 10^{9} \, \mathrm{cm}$ and
$n_{\theta} = 128$ equidistant cells in angular direction. For the
neutrino energies, we used a logarithmic grid with $n_e = 10$ bins up
to $240 \, \mathrm{MeV}$.
\pcd{Unlike the model set, the simulations in the test set are not 1D because we need to 
extract the gravitational wave signal, which is a multi-dimensional effect. For each simulation
we extract the gravitational wave signal, $h_+(t)$,  by means of the quadrupole formula and compute the 
time evolution of the surface gravity, $r(t)$.}
